\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry} 
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{accents}


\setlength{\oddsidemargin}{0in}
\setlength{\textwidth}{6.5in}
\setlength{\topmargin}{-.55in}
\setlength{\textheight}{9in}
\pagestyle{empty}
\renewcommand \d{\displaystyle}
\renewcommand \a{\shortstack{$\rightarrow$\\$u$}}
\renewcommand \b{\shortstack{$\rightarrow$\\$v$}}

\begin{document}
\noindent Math 4510

\noindent Topology

\vspace{.2in}
\begin{center}
Problem Set 8
\end{center}

 \begin{enumerate}%\setlength{\itemindent}{-1.5em}
 \item(\#5 in 6.2) Prove Theorem 6.2.4: Let $A_{\tau_A}$ be a connected subspace of a space $X_{\tau}$, and let $B$ be a subset of $X$ with $A\subseteq B\subseteq \text{Cl($A$)}$. Then $B$ is also connected in the subspace topology.
 
 Proof: Let $A_{\tau_A}$ be a connected subspace of a space $X_{\tau}$ and $B$ be a subset of $X$ with $A \subseteq B \subseteq \text{Cl}(A)$. By theorem 6.2.3, we also know that $\text{Cl}(A)$ is connected.
 
 Assume by way of contradiction that $B$ is disconnected. That is, there exist non-empty subsets of $B$, $\beta_1$, $\beta_2$ open in $\tau_B$ such that $\beta_1 \cup \beta_2 = B$ and $\beta_1 \cap \beta_2 = \emptyset$.
 
 Since $\beta_1$ and $\beta_2$ are $\tau_B$-open, there exist $\tau$-open sets $U_1, U_2$ such that
 \[\beta_1 = U_1 \cap B\]
 \[\beta_2 = U_2 \cap B\]
 And since $A \subseteq B$, we have that $A = A \cap B$. So 
 \[A = A \cap [(U_1 \cap B) \cup (U_2 \cap B)]\]
 \[ = (A \cap (U_1 \cap B)) \cup (A \cap (U_2 \cap B))\]
 \[ = (A \cap B \cap U_1) \cup (A \cap B \cap U_2)\]
 \[ = (A \cap U_1) \cup (A \cap U_2)\]
\[ = A \cap (U_1 \cup U_2)\]
 Let $V_1 = A \cap U_1$ and $V_2 = A \cap U_2$; which are open in $\tau_A$ since $U_1$ and $U_2$ are $\tau$-open. So we have
 \[A = V_1 \cup V_2\]
 
 Now we will show that $V_1, V_2$ are non-empty. Recall that $\text{Cl}(A) = A \cup A'$.
 
 Since $\beta_1 \neq \emptyset$ and $\beta_1 = U_1 \cap B$, we have that $U_1$ is nonempty. Let $x_0 \in B$. Then $x_0 \in \beta_1 \cup \beta_2$, and since $\beta_1 \cap \beta_2 = \emptyset$, $x_0$ is either exclusively in $\beta_1$ or $\beta_2$. Suppose without loss of generality that $x_0 \in \beta_1$. 
 Then $x_0 \in U_1 \cap B$, and so $x_0 \in U_1$. Additionally, since $B \subseteq \text{Cl}(A)$, $x_0 \in \text{Cl}(A)$. Then every neighborhood $N_{x_0}$ of $x_0$ intersects $A$ nontrivially, so $x_0 \in A$. Then we have $x_0 \in A$ and $x_0 \in U_1$, so $x_0 \in A \cap U_1 = V_1$.
 
 So we have that $V_1 = A \cap U_1$ is non-empty. A similar argument holds for $V_2$.
 
 Recall that $\beta_1 \cap \beta_2 = \emptyset$ and that $\beta_1 = U_1 \cap B$ and $\beta_2 = U_2 \cap B$, so
 \[\beta_1 \cap \beta_2 = (U_1 \cap B) \cap (U_2 \cap B)\]
 \[ = U_1 \cap B \cap U_2 \cap B\]
 \[ = B \cap B \cap (U_1 \cap U_2)\]
 \[ = B \cap (U_1 \cap U_2)\]
 \[ = \emptyset\]
 and since $B \neq \emptyset$, we have that $U_1 \cap U_2 = \emptyset$.
 
 Notice that
 \[V_1 \cap V_2 = (A \cap U_1)  \cap (A \cap U_2)\]
 \[ = A \cap A \cap U_1 \cap U_2\]
 \[ = A \cap (U_1 \cap U_2)\]
 \[ = A \cap \emptyset\]
 \[ = \emptyset \]
 So we have two $\tau_A$-open sets $V_1, V_2$ such that $V_1 \cup V_2 = A$ and $V_1 \cap V_2 = \emptyset$. So by definition, we have that $A$ is disconnected, which contradicts the hypothesis that $A$ is connected, and thus, $B$ must be a connected space of $X_{\tau}$.
 
 
 
 
\item Let $X_{\tau}$ be a space with the property that given any $x\in X$ and any neighborhood $U$ of $x$, there is a neighborhood $V$ of $x$ such that Cl($V$) is a proper subset of $U$. 
\begin{enumerate}
\item Give an example that shows that $X$ need not be connected. 
\newline

Consider a set $X$ equipped with the discrete topology and let $x \in X$. Then any subset $U \subseteq X$ that contains $x$ is a neighborhood of $x$. Then for any proper subset $V$ of $U$, $\text{Cl}(V) = V$ in the discrete topology, and so we have $\text{Cl}(V) \subset U$. So $X_{\mathcal{D}}$ satisfies these conditions. Additionally, as long as $\text{Card}(X) \geq 2$, we have that $X_{\mathcal{D}}$ is disconnected.
\newline



\item If we add the condition that for every $x\in X$ and every neighborhood $U$ of $x$ there is a connected neighborhood $V_x$ of $x$ such that $x\in V_x\subseteq \text{Cl($V_x$)}\subseteq U$, is this sufficient to make $X$ connected? Explain.
\newline

No. Let $X$ be a space equipped with the discrete topology where $\text{Card}(X) > 2$. Let $x \in X$ and $U$ be a neighborhood of $x$. Let $V_x = \{x\}$ be the neighborhood of $x$ that contains only $x$. Since $X$ is equipped with the discrete topology, $\text{Cl}(V_x) = V_x$ and notice that $V_x$ is trivially connected and $x \in \{x\} \subseteq U$. However, since $X$ is a discrete topological space, we have that $X$ is disconnected.


\end{enumerate}
%\item (\#2 in 6.4) Is $\mathbb{R}_{\mathcal{L}}$ path-connected? Justify your conclusion.
\item(\#6 in 6.4) Prove that if $X_{\tau}$ is path-connected and $\tau' \subseteq \tau$, then $X_{\tau'}$ is also path-connected.

Proof: Let $X_{\tau}$ and $X_{\tau'}$ be topological spaces where $\tau' \subseteq \tau$ and $X_{\tau}$ is path-connected. 
Since $\tau' \subseteq \tau$, we have that the identity map $i_x: X_{\tau} \to X_{\tau'}$ is continuous. And since $X_{\tau}$ is path-connected, we have that $X_{\tau'}$ is also path-connected since $X_{\tau'}$ is the continuous image of a path-connected space.



\item Prove that any quotient space of a path-connected space is path-connected. That is, if $X_{\tau}$ is a path-connected space and $\sim$ is an equivalence relation on $X$, then the quotient space $X/\sim$ is path-connected.

Proof: Let $X_{\tau}$ be a path-connected space, $\sim$ be an equivalence relation of $X$ and let $X/\sim$ be the quotient space.
Let $\nu: X_{\tau} \to X_{/\sim}$ be the natural map. We have that $\nu$ is continuous, and we wish to show that $\nu$ is surjective. Suppose by way of contradiction that $\nu$ is not surjective. That is, there exists some element $[x] \in X_{/\sim}$ such that $\nu^{-1}([x]) = \emptyset$. But from the definition of the natural map, $\nu^{-1}([x]) = x \in X$. So $\nu$ is surjective. Since path-connectedness is a strong topological property and $\nu$ is continuous, we have that $X_{/\sim}$ is also path-connected.


\end{enumerate}

\noindent \textbf{Bonus} Show that if $U$ is an open connected subset of $\mathbb{R}^2$, then $U$ is path-connected. (Hint: Show that given a point $x_0\in U$, the set of points in $U$ that can be joined to $x_0$ by a path in $U$ is both open and closed.)
\end{document}
